---
title: "Auscultation: BN report"
author: " Author 1"
date:  " "
output: 
  html_document:
    toc: false
  word_document:
    reference_docx: "template.docx"
params:
      dataNow: NA
      myNotes: NA
      tavola1: !r  NA
      tavola2: !r  NA
      figura1: !r  NA
      figura2: !r  NA  
      current_evi: !r NA
      spe_sen_LS: !r NA
      effe_size_stat: !r NA
      release_cur:  "0.0"
---

Today: `r params$dataNow`     
Current release: rel.  `r params$release_cur`    



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      opts.label="kill_prefix")
library(stringr)
library(magrittr)
library(tidyverse)
library(ggplot2)
library(dplyr)
 
save(params,file="params.RData")
```




```{r,echo=FALSE,eval=FALSE,results='hide'}
rmarkdown::render(input = "www/BN_auscult_report.Rmd", 
                  output_format = "html_document", 
        params = list( dataNow =  paste0(date()),
                       myNotes =  paste0("Cosa combini?","ciao"),
                       tavola1  = get("iris",envir= .GlobalEnv),
                       tavola2  = get("iris",envir= .GlobalEnv),
                       figura1 =  get("figu1",envir= .GlobalEnv),
                       figura2 =  get("figu2",envir= .GlobalEnv),
                       current_evi = get("current_evi",envir= .GlobalEnv)), 
             intermediates_dir = "www",
            output_dir = "www", 
            output_file = "BNreport")
```
 
 
 
 
 
 
 
## Notes 

```{r,comment=NA}
cat(params$myNotes)
 
```
 
 
 
## Prior and posterior probability values.

The initial probability is the marginal distribution of disease (empty evidence).   

The final probability is conditioned to 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi $$ 
where $\xi$ is the collected evidence beyond the two compulsory crackles nodes
VC Basal and VC sym.


```{r}
print(params$tavola1,df_print="kable")
```


BF values

```{r}
print(params$tavola2,df_print="kable")
```



## Figures

```{r}
print(params$figura1)
```


```{r,results='asis'}
cat("\n<br><br>\n")
```


```{r}
print(params$figura2)
```






## Informed nodes (evidence)

Here below, the evidence entered into the Bayesian Network and selected 
parameters values are shown.

Sensitivity and specificiy values:

```{r}
params$spe_sen_LS
```


Evidence:


```{r,echo=F}
cat("\n")
etichette <-  names(params$current_evi)
valoriEv <- as.character(params$current_evi)
mancanti <- valoriEv== "NA"
 
res <- sort(paste(etichette[!mancanti],"=", valoriEv[!mancanti]))
cat(res, sep="\n")
cat("\n")
```






# Effect size: informed evidences

In this section the leave-one-out effect (Loo) 
and the switch-one-state (Sos) effect are evaluated 
for every node for which evidence is provided.



The first two tables below, are obtained with an initial distribution on diseases
conditioned to the two compulsory crackles variables   
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev $$ 
while the final distribution is obtained by also conditioning to all other collected evidences $\xi$
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi $$ 


```{r}
print(params$effe_size_stat$res_all_evid$tavolaPro,
      df_print="kable")
```


BF values, crackles as initial reference, original provided evidence:

```{r}
print(params$effe_size_stat$res_all_evid$tavolaBF,
      df_print="kable")
```




## Informed evidences: Loo

Below ratios of posterior probability and of BF are printed
after deleting evidence in turn one node at a time.


Posterior probability ratios: 
```{r}
mygraphprobloo <- diverging_bchart_loo(params$effe_size_stat,
                                       type_sco=c("tavolaPro","tavolaBF")[1])
numeroBarre <- length(params$effe_size_stat[["res_loo"]])
dimensioHeight <- min(2 + 10*(numeroBarre/30), 12)
```

```{r,fig.height=dimensioHeight,fig.width=10}
                                 
print(mygraphprobloo)  
```



Bayes Factor ratios:

```{r,fig.height=dimensioHeight,fig.width=10}
mygraphBFloo <- diverging_bchart_loo(params$effe_size_stat,
                                   type_sco=c("tavolaPro","tavolaBF")[2])

print(mygraphBFloo)  
```



 


### Loo: full table


Below the node removed from evidences is printed and the 
implied tables are shown.

The initial distribution on diseases is conditioned on 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi $$ 
The final  distribution on diseases is conditioned on 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge (\xi\setminus\delta_i) $$ 
thuis the variable $\delta_i$ has been deleted from evidence.


```{r,comment=NA}
knitr::opts_chunk$set(opts.label="kill_prefix")
for(aux in seq_along(params$effe_size_stat$res_loo)){
  msg <-  paste0("Deleted evidence: ",params$effe_size_stat$res_loo[[aux]]$deletedEvidence)
  cat("--------------------------------------------------------------------------------\n")
  cat(msg,"\n")
  cat("\n")
  print(params$effe_size_stat$res_loo[[aux]]$tavolaPro)
  cat("\n\n")
  print(params$effe_size_stat$res_loo[[aux]]$tavolaBF)
  cat("\n\n")
}

```







## Informed evidences: Sos

Here each node in the evidence  switches its state to another one which
is not equal to the collected evidence.


```{r}
numeroBarre <- length(params$effe_size_stat[["res_switchin"]])
dimensioHeight <- min(2+ 10*(numeroBarre/50),12)
```


Posterior probability ratios: 
 
```{r,fig.height=dimensioHeight,fig.width=10}
mygraphprobsos <- diverging_bchart_sos(params$effe_size_stat,
                                       type_sco=c("tavolaPro","tavolaBF")[1])
                                 
print(mygraphprobsos)  
```



Bayes Factor ratios:

```{r,fig.height=dimensioHeight,fig.width=10}
mygraphBFsos <- diverging_bchart_sos(params$effe_size_stat,
                                   type_sco=c("tavolaPro","tavolaBF")[2])

print(mygraphBFsos)  
```







### Sos: full tables

The initial distribution on diseases is conditioned on 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi $$ 
The final  distribution on diseases is conditioned on 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi(\sigma_{i,j}) $$ 
thus the evidence has been modified because variable   $\delta_i$ was switched into its state $j$,
a switch indicated as $\xi(\sigma_{i,j})$.




```{r,comment=NA}
knitr::opts_chunk$set(opts.label="kill_prefix")
dimen_sos <- length(params$effe_size_stat$res_switch)

for(aux in seq_along(params$effe_size_stat$res_switch)){
  msg <-  paste0('Node "',params$effe_size_stat$res_switch[[aux]]$node,'" switched state to "',
                 params$effe_size_stat$res_switch[[aux]]$state,'"\n\n')
  cat("--------------------------------------------------------------------------------\n")
  cat(msg,"\n")
  cat("\n")
  print(params$effe_size_stat$res_switch[[aux]]$tavolaPro)
  cat("\n\n")
  print(params$effe_size_stat$res_switch[[aux]]$tavolaBF)
  cat("\n\n")
}

```



 










# Effect size: inputed missing evidence


In this section the reference distribution is
made by the posterior distribution after all the available evidence is entered.
Among the missing variables (outside the collected evidence) in turn one is entered with 
value equal to one among possible states and then the  posterior distribution is calculated.


The initial probability of disease is conditioned to 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi$$ 
two compulsory crackles nodes, and the collected evidence.   

The final probability is conditioned to 
$$EE\_AuscVC\_Basal  \wedge EE\_AuscVC\_Sym\_same\_lev \wedge \xi \wedge \mathcal{I}_{j,k}$$ 
that is  EE auscultated crackles and collected evidence $\xi$
and the imputed variable $j$ in its state $i$, which is $\mathcal{I}_{j,k}$ .



Posterior probability changes (ratios): 

```{r}
numeroBarre <- length(params$effe_size_stat[["res_missing"]])
dimensioHeight <- min(2+ 10*(numeroBarre/50),12)
```

```{r,fig.height=dimensioHeight,fig.width=10}
 
mygraphprob <- diverging_bchart_miss(params$effe_size_stat,
                                     type_sco=c("tavolaPro","tavolaBF")[1])
print(mygraphprob)  
```



Bayes Factor:

```{r,fig.height=dimensioHeight,fig.width=10}
mygraphBF <- diverging_bchart_miss(params$effe_size_stat,
                                   type_sco=c("tavolaPro","tavolaBF")[2])
print(mygraphBF)  
```



### Missing evidence: full output
    
    

    
```{r,comment=NA}
knitr::opts_chunk$set(opts.label="kill_prefix")
dimen_moi <- length(params$effe_size_stat$res_missing)

for(aux in seq_along(params$effe_size_stat$res_missing)){
  msg <-  paste0('Node "',params$effe_size_stat$res_missing[[aux]]$node,'" missing,\nimputed state= "',
                 params$effe_size_stat$res_missing[[aux]]$state,'"\n\n')
  cat("--------------------------------------------------------------------------------\n")
  cat(msg,"\n")
  cat("\n")
  print(params$effe_size_stat$res_missing[[aux]]$tavolaPro)
  cat("\n\n")
  print(params$effe_size_stat$res_missing[[aux]]$tavolaBF)
  cat("\n\n")
}

```




```{r,results='asis'}
cat("<br><br><br><br><br><br><br>")
```

















